### 2017-08-09 Tex_Dissertation/MSc_dissertation.tex
endofday

@@

Althought the GBDT's at first seem to be better candidate for a more precise mass calculation, the BDT's 
proved to be the ones that offered a better one. That is because the resulting number of events in the BDT 
method are more than the ones in GBDT implying that having stronger signal than better separation between 
signal background is preferable to the case of the mass calculation of the $\tilde{t}$ in CLIC experiment.

>>>>

His comments and technical help proved to be valuable, thus I owe a big thank you to Alan Taylor (UoE).

@@

Althought the GBDT's at first seem to be the best candidate for a more precise mass calculation, the BDT's 
proved to be the ones that offered a better one. That is because the resulting number of signal events in the BDT 
method are more than the ones in GBDT implying that having stronger signal than better separation between 
signal-background is preferable in the case of the mass calculation of the $\tilde{t}$ in CLIC experiment.
